

I would like to thanks Daniel Den Hartog and Mark Nornberg for advising and mentoring me through my grad school years. Their expertise, guidance, and thoughtful feedback has been instrumental in the completion of this thesis. I would like to thank John Sarff for welcoming me to the MST group. I am indebted to my committee members Carl Sovenic and Paul Terry for their inputs and for pointing out both the flaws the potentials in my work.

I would like to thank Darren Craig for his insights and knowledge regarding ion Doppler spectrometer and Santhosh Kumar for helping me get started all those years ago. Also thanks to MST scientists Jay Anderson and Karsten McCollom for patiently sharing their knowledge of RFP physics with me. I would further like to thank the staff engineers, including but not limited to Peter Weix, Mike Borchardt, Steve Oliva, Alex Squitieri, and Pual Wilhite, who has been integral to the successful operations of MST and it's diagnostics during my experiments.

Special thanks to fellow graduate students Takashi Nishizawa and John Boguski who worked on the CHERS diagnostic with me, as well as postdoc Xinde Feng who helped to bring the DNB back online. Without you, I would not have had measurements to show. Thanks also to Eli Parke, James Duff, Steph Kubala and Dylan Adams for operating their diagnostics which contributed critical input data to my work.
\begin{CJK*}{UTF8}{gbsn}

I would not be here today if not for the support of my family. I would especially like to thank my parents (Xiaoxing Xing) and (Yan Wang) who were not fans of the PhD career but supported my path nonetheless. 

\end{CJK*}

Last but least, I would like to thank David Hammer, Peter Titus, Robert Ellis and Stewart Zweben for putting me onto the path of fusion research. 

\clearpage