\begin{refsection}


\chapter{Results: Ion Thermal Transport in MST's PPCD plasmas}\label{ch:results}



This chapter describes the main body of results and discoveries made during this modeling effort. Overall, this transport model based on classical effects can adequately describe the temperature evolution in the core, but needs an extra \textit{ad hoc} heating term localized in the edge to explain the edge ion temperature measurements. This chapter will get to this result in three steps. First is a discussion of the neutral dynamics, including the charge exchange and impact ionization rates, in PPCD plasmas. Some unintuitive effects on core neutral dynamics from adding an \textit{ad hoc} heating term in the edge are illustrated. This is followed by a discussion of the inward pinch needed to account for density evolution, how it is correlated with the \ecb flux, its context as part of the net radial flow, and how it affects the thermal transport. Finally, I discuss the comparison between model and data, with and without an \textit{ad hoc} term in the edge. The chosen profile of this anomalous heating term is explained and motivated by proposed physical mechanisms. 
\input{ion_transport_results/neutrals.tex}
\input{ion_transport_results/pinch.tex}
\input{ion_transport_results/heating.tex}

\section{Summary}

Experimental results show the 1-D ion thermal transport model adequately predicts the ion temperature evolution in the core, but needs an \adhoc term in the gradient region to match observations there. Of particular importance to the model is the neutral dynamics as calculated via the Monte-Carlo simulation code DEGAS2. This simulation is important in calculating the charge exchange loss from the core. The results indicates that the neutral population in the core is 'warm' and the charge exchange loss is somewhat hollow. The ionization of neutrals are found to 'recover' some of the energy lost to the neutral fluid, but this results in decrease in temperature. The source rate geometry and continuity equations calculations finds that PPCD plasmas under goes an inward pinch during the first milliseconds, which contributes to core temperature via compression. However, the net particle flux at the edge is outwards and represents a significant loss term. When compared to ion temperature measurements, the model is found to be unable to match the observation in the gradient region unless an radially local \adhoc heating term is added. Comparisons are drawn between the \adhoc term needed and estimates of fluctuation induced heating and found to be plausible.


\printbibliography
\end{refsection}